### 2023-03-13 intro.qmd
some leftover stuff

plt_original = plot(mod, counterfactual_data; zoom=0, colorbar=false, title="(a)")
display(plt_original)
```

@@

## Generate counterfactual

@@

candidates = findall(ys.==0)
chosen_individuals = rand(candidates, Int(round(μ*length(candidates))))
X′ = copy(X)
y′ = copy(ys)
factuals = select_factual(counterfactual_data,chosen_individuals)
outcome = generate_counterfactual(factuals, 1, counterfactual_data, mod, gen; initialization=:identity)
X′[:,chosen_individuals] = reduce(hcat, @.(selectdim(counterfactual(outcome), 3, 1)))
y′[chosen_individuals] = reduce(vcat,@.(selectdim(counterfactual_label(outcome),3,1)))
counterfactual_data′ = CounterfactualData(X′,y′')
plt_single = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(b)")
display(plt_single)
```

## Retrain

@@

mod = Models.train(mod, counterfactual_data′)
plt_single_retrained = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(c)")
display(plt_single_retrained)
```

## Repeat

@@

```{julia}
i = 2
while i <= 10
    counterfactual_data′ = CounterfactualData(X′,y′')
    candidates = findall(y′.==0)
    chosen_individuals = rand(candidates, Int(round(μ*length(candidates))))
    Models.train(mod, counterfactual_data′)
    factuals = select_factual(counterfactual_data′,chosen_individuals)
    outcome = generate_counterfactual(factuals, 1, counterfactual_data′, mod, gen; initialization=:identity)
    X′[:,chosen_individuals] = reduce(hcat, @.(selectdim(counterfactual(outcome), 3, 1)))
    y′[chosen_individuals] = reduce(vcat,@.(selectdim(counterfactual_label(outcome),3,1)))
    i += 1
end
plt_single_repeat = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(d)")
```

>>>>

plt_original = plot(
    mod, counterfactual_data; zoom=0, colorbar=false, title="(a)", 
    legend=false, axis=nothing, size=(400,400)
)
display(plt_original)
```

@@

### Generate Counterfactual

@@

candidates = findall(ys.==0)
chosen_individuals = rand(candidates, Int(round(μ*length(candidates))))
X′ = copy(X)
y′ = copy(ys)
factuals = select_factual(counterfactual_data,chosen_individuals)
outcome = generate_counterfactual(factuals, 1, counterfactual_data, mod, gen; initialization=:identity)
X′[:,chosen_individuals] = reduce(hcat, @.(selectdim(counterfactual(outcome), 3, 1)))
y′[chosen_individuals] = reduce(vcat,@.(selectdim(counterfactual_label(outcome),3,1)))
counterfactual_data′ = CounterfactualData(X′,y′')
plt_single = plot(
    mod,counterfactual_data′;zoom=0,colorbar=false,title="(b)",
    legend=false, axis=nothing, size=(400,400)
)
display(plt_single)
```

### Retrain

@@

mod = Models.train(mod, counterfactual_data′)
plt_single_retrained = plot(
    mod,counterfactual_data′;zoom=0,colorbar=false,title="(c)",
    legend=false, axis=nothing, size=(400,400)
)
display(plt_single_retrained)
```

### Repeat

@@

```{julia}
i = 2
while i <= 10
    counterfactual_data′ = CounterfactualData(X′,y′')
    candidates = findall(y′.==0)
    chosen_individuals = rand(candidates, Int(round(μ*length(candidates))))
    Models.train(mod, counterfactual_data′)
    factuals = select_factual(counterfactual_data′,chosen_individuals)
    outcome = generate_counterfactual(factuals, 1, counterfactual_data′, mod, gen; initialization=:identity)
    X′[:,chosen_individuals] = reduce(hcat, @.(selectdim(counterfactual(outcome), 3, 1)))
    y′[chosen_individuals] = reduce(vcat,@.(selectdim(counterfactual_label(outcome),3,1)))
    i += 1
end
plt_single_repeat = plot(
    mod,counterfactual_data′;zoom=0,colorbar=false,title="(d)",
    legend=false, axis=nothing, size=(400,400)
)
```

### 2023-03-13 sections/experiments/mitigation_strategies.qmd
uh
some leftover stuff

# Mitigation Strategies

@@

```{julia}
using Serialization
results = Serialization.deserialize(joinpath(output_path,"results_synthetic.jls"))
```

>>>>

# Results: Mitigation Strategies

@@

```{julia}
results = Serialization.deserialize(joinpath(output_path,"results_synthetic.jls"))
```

```{julia}
#| echo: false
Plots.scalefontsizes(2)
df_plot = results[:overlapping].output |>
    df -> filter(:name => ==(:mmd), df) |>
    df -> filter(:model => ==(:FluxEnsemble), df) |>
    df -> filter(:scope => ==(:domain), df) |>
    df -> filter(:n => >(0), df)

df_plot.generator .= string.(df_plot.generator)
df_plot.generator .= replace(
    df_plot.generator, 
    "Generic" => "Gen.(γ=0.5)",
    "Generic_conservative" => "Gen.(γ=0.9)",
    "ClapROAR" => "ClaPROAR"
)

ylims = (0, 1.2 * maximum(df_plot.value))

anim = @animate for i in sort(unique(df_plot.n))
    df = filter(:n => ==(i), df_plot) |>
        df -> combine(groupby(df, :generator), :value => mean, :value => std)
    plt = bar(
        string.(df.generator), df.value_mean, 
        c=:blues, 
        linecolor=ifelse.(df.generator .∈ [["Gravitational", "ClaPROAR", "Gen.(γ=0.9)"]], :orange, nothing),
        linestyle=ifelse.(df.generator .∈ [["Gravitational", "ClaPROAR"]], :solid, :dot),
        lw=5, widen=false,
        legend=false,
        ylims = ylims,
        title = "Number of rounds: $(i)",
        xtickfontsize = 10,
    )
    n_gen = length(unique(df.generator))
    plot!((0:(n_gen-1)) .+ 0.5, df.value_mean, yerror=df.value_std, ms=10, color="transparent")
    scatter!((0:(n_gen-1)) .+ 0.5, df.value_mean, ms=10, c=:blues)
end
gif(anim, "dev/presentation/www/mitigation_domain.gif", fps=0.5)
Plots.scalefontsizes()
```

```{julia}
#| echo: false
Plots.scalefontsizes(2)
df_plot = results[:overlapping].output |>
    df -> filter(:name => ==(:model_performance), df) |>
    df -> filter(:model => ==(:FluxEnsemble), df) |>
    df -> filter(:scope => ==(:model), df) |>
    df -> filter(:n => >(0), df)

df_plot.generator .= string.(df_plot.generator)
df_plot.generator .= replace(
    df_plot.generator, 
    "Generic" => "Gen.(γ=0.5)",
    "Generic_conservative" => "Gen.(γ=0.9)",
    "ClapROAR" => "ClaPROAR"
)

ylims = (1.2 * minimum(df_plot.value), 0)

anim = @animate for i in sort(unique(df_plot.n))
    df = filter(:n => ==(i) ,df_plot) |>
        df -> combine(groupby(df, :generator), :value => mean, :value => std)
    plt = bar(
        string.(df.generator), df.value_mean, 
        c=:blues, 
        linecolor=ifelse.(df.generator .∈ [["Gravitational", "ClaPROAR", "Gen.(γ=0.9)"]], :orange, nothing),
        linestyle=ifelse.(df.generator .∈ [["Gravitational", "ClaPROAR"]], :solid, :dot),
        lw=5, widen=false,
        legend=false,
        ylims = ylims,
        title = "Number of rounds: $(i)",
        xtickfontsize = 10,
    )
    n_gen = length(unique(df.generator))
    plot!((0:(n_gen-1)) .+ 0.5, df.value_mean, yerror=df.value_std, ms=10, color="transparent")
    scatter!((0:(n_gen-1)) .+ 0.5, df.value_mean, ms=10, c=:blues)
end
gif(anim, "dev/presentation/www/mitigation_performance.gif", fps=0.5)
Plots.scalefontsizes()
```

### 2023-03-13 sections/experiments/real_world.qmd
uh
some leftover stuff

# Real-World Data

@@

>>>>

# Results: Real-World Data

@@

```{julia}
#| echo: false
Plots.scalefontsizes(2)
df_plot = results[:credit_default].output |>
    df -> filter(:name => ==(:mmd), df) |>
    df -> filter(:model => ==(:FluxEnsemble), df) |>
    df -> filter(:scope => ==(:model), df) |>
    df -> filter(:n => >(0), df)

ylims = (0, 1.2 * maximum(df_plot.value))

anim = @animate for i in sort(unique(df_plot.n))
    df = filter(:n => ==(i) ,df_plot) |>
        df -> combine(groupby(df, :generator), :value => mean, :value => std)
    plt = bar(
        string.(df.generator), df.value_mean, c=:blues, lw=0, widen=false,
        legend=false,
        ylims = ylims,
        title = "Number of rounds: $(i)"
    )
    n_gen = length(unique(df.generator))
    plot!((0:(n_gen-1)) .+ 0.5, df.value_mean, yerror=df.value_std, ms=10, color="transparent")
    scatter!((0:(n_gen-1)) .+ 0.5, df.value_mean, ms=10, c=:blues)
end
gif(anim, "dev/presentation/www/real_world_model.gif", fps=0.5)
Plots.scalefontsizes()
```

```{julia}
#| echo: false
Plots.scalefontsizes(2)
df_plot = results[:credit_default].output |>
    df -> filter(:name => ==(:model_performance), df) |>
    df -> filter(:model => ==(:FluxEnsemble), df) |>
    df -> filter(:scope => ==(:model), df) |>
    df -> filter(:n => >(0), df)

ylims = (1.2 * minimum(df_plot.value), 0)

anim = @animate for i in sort(unique(df_plot.n))
    df = filter(:n => ==(i) ,df_plot) |>
        df -> combine(groupby(df, :generator), :value => mean, :value => std)
    plt = bar(
        string.(df.generator), df.value_mean, c=:blues, lw=0, widen=false,
        legend=false,
        ylims = ylims,
        title = "Number of rounds: $(i)"
    )
    n_gen = length(unique(df.generator))
    plot!((0:(n_gen-1)) .+ 0.5, df.value_mean, yerror=df.value_std, ms=10, color="transparent")
    scatter!((0:(n_gen-1)) .+ 0.5, df.value_mean, ms=10, c=:blues)
end
gif(anim, "dev/presentation/www/real_world_performance.gif", fps=0.5)
Plots.scalefontsizes()
```

### 2023-03-13 sections/experiments/synthetic.qmd
some leftover stuff

# Synthetic Data {#sec-app-synthetic}

@@

>>>>

# Results: Synthetic Data {#sec-app-synthetic}

@@

```{julia}
#| echo: false
Plots.scalefontsizes(2)
df_plot = results[:overlapping].output |>
    df -> filter(:name => ==(:mmd), df) |>
    df -> filter(:model => ==(:FluxEnsemble), df) |>
    df -> filter(:scope => ==(:domain), df) |>
    df -> filter(:n => >(0), df)

ylims = (0, 1.2 * maximum(df_plot.value))

anim = @animate for i in sort(unique(df_plot.n))
    df = filter(:n => ==(i) ,df_plot) |>
        df -> combine(groupby(df, :generator), :value => mean, :value => std)
    plt = bar(
        string.(df.generator), df.value_mean, c=:blues, lw=0, widen=false,
        legend=false,
        ylims = ylims,
        title = "Number of rounds: $(i)"
    )
    n_gen = length(unique(df.generator))
    plot!((0:(n_gen-1)) .+ 0.5, df.value_mean, yerror=df.value_std, ms=10, color="transparent")
    scatter!((0:(n_gen-1)) .+ 0.5, df.value_mean, ms=10, c=:blues)
end
gif(anim, "dev/presentation/www/synthetic_domain.gif", fps=0.5)
Plots.scalefontsizes()
```

```{julia}
#| echo: false
Plots.scalefontsizes(2)
df_plot = results[:overlapping].output |>
    df -> filter(:name => ==(:model_performance), df) |>
    df -> filter(:model => ==(:FluxEnsemble), df) |>
    df -> filter(:scope => ==(:model), df) |>
    df -> filter(:n => >(0), df)

ylims = (1.2 * minimum(df_plot.value), 0)

anim = @animate for i in sort(unique(df_plot.n))
    df = filter(:n => ==(i) ,df_plot) |>
        df -> combine(groupby(df, :generator), :value => mean, :value => std)
    plt = bar(
        string.(df.generator), df.value_mean, c=:blues, lw=0, widen=false,
        legend=false,
        ylims = ylims,
        title = "Number of rounds: $(i)"
    )
    n_gen = length(unique(df.generator))
    plot!((0:(n_gen-1)) .+ 0.5, df.value_mean, yerror=df.value_std, ms=10, color="transparent")
    scatter!((0:(n_gen-1)) .+ 0.5, df.value_mean, ms=10, c=:blues)
end
gif(anim, "dev/presentation/www/synthetic_performance.gif", fps=0.5)
Plots.scalefontsizes()
```

```{julia}
df = DataFrame(group=["A", "B", "C"], total=[7.7, 4.6, 5.1], std_error = [0.04, 0.05, 0.06])
bar(df.group, df.total, c=:blues, lw=0, widen=false)
plot!(1/2:(ncol(df)-1/2), df.total, lw=0, yerror=20*df.std_error, ms=10)
```
